---
title: "Video view analysis"
format: html
knitr:
  opts_knit:
    root.dir: ".."
---

# Video view analysis

This report practices Quarto, `dplyr` aggregation, and a reproducible workflow
on the `video_view.csv` dataset. Text and code live in one file.

## Load the data

We use the local file if it exists, and download it once otherwise.

```{r}
#| message: false
library(tidyverse)

data_path <- "data/video_view.csv"

if (!file.exists(data_path)) {
  dir.create("data", showWarnings = FALSE)
  data_url <- paste0(
    "https://raw.githubusercontent.com/hannesdatta/",
    "course-dprep/refs/heads/main/material/tutorials/r-bootcamp-rev/",
    "video_view.csv"
  )
  download.file(data_url, data_path)
}

videos <- read_csv(data_path)
```

## Inspect

```{r}
glimpse(videos)
```

## Creator summary

How do creator-level metrics differ across creators?

```{r}
creator_summary <- videos %>%
  group_by(creator_id) %>%
  summarise(
    videos_n          = n(),
    impressions_total = sum(impressions_n, na.rm = TRUE),
    watch_rate_avg    = mean(watch_rate, na.rm = TRUE)
  ) %>%
  arrange(desc(impressions_total))

head(creator_summary, 10)
```

## Top-watched videos

Which reasonably-visible videos have the highest watch rate?

```{r}
top_watch <- videos %>%
  select(video_id, creator_id, impressions_n, watch_rate) %>%
  filter(impressions_n >= 50) %>%
  arrange(desc(watch_rate))

head(top_watch, 10)
```

## Creator engagement

Ranking creators by average engagement (`watched_n / impressions_n`) instead of
raw reach.

```{r}
creator_engagement <- videos %>%
  mutate(engagement = watched_n / impressions_n) %>%
  group_by(creator_id) %>%
  summarise(mean_engagement = mean(engagement, na.rm = TRUE)) %>%
  arrange(desc(mean_engagement))

head(creator_engagement, 10)
```
